---
title: "Alcohol vs Seat choice"
author: "Marta Marriott"
date: "Spring 2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  The data from the boxplot displays the box representing the students sitting in the back to be much larger than the front and middle sections, suggesting that students who choose to sit in the back have a higher likelihood of consuming alcohol.
 
 
## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=ucdavis1)
```
 The numerical data presented, shows the number of drinks consumed  by students in the different seating areas of the class per week, showing the students seated in the back consumed more than those seated in the middle and the front. The students seated in the front consumed 1.78 drinks per week, the students seated in the middle consumed 3.33 drinks, and those in the back consumed 8.55 drinks per week.


## Inferential Tests

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```
The graph displays a significant result, as the numbers are much smaller than 0.05.

```{r}
plot(TukeyHSD(model1))
```

This graph shows the amount of differences where a students sits drinks. The data presented in the graph shows, students who sit in the front and students who sit in the back drink roughly about the same or what what be considered a moderate amount of drinks per week. However, the students who sit in the back consume a larger amount of drinks per week than those who sit in the front and middle.

## Conclusions


